---
title: "Intro to my package"
output:
  rmarkdown::html_vignette:
    toc: yes
    #theme: cayman
    #toc_float: yes

vignette: >
  %\VignetteIndexEntry{Intro to my package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SHollizeckPackage)
```

# Introduction
This package contains all of the functions written in R for my PhD. These will be non thematically seperated functions. For an overview of the workflows it is probably smart to look at the markdowns generated for sample analysis.


## Colours
This section has to do with different colors functions
`make_shades()`, `plot_colours()` and `random_colours()` allows easy acces to standard requests that you have

```{r shades}
shades <- make_shades("goldenrod", 5)
```
this will generate different shades of the color "goldenrod"

which you can then visualize with
```{r plot, fig.width=7, fig.align="center"}
plot_colours(shades)
```

This function however works with any colours that you throw at it, for example 10 random colours from the function

```{r random colors, fig.width=7, fig.align="center"}
plot_colours(random_colors(10))
```

Then if you do not like the next to each other visualization, you can use `draw_color_circle()` to view how R will use them with recycling

```{r circle, fig.width=7, fig.height=7, fig.align="center"}
draw_color_circle(shades,lwd=50)
```


or directly with random colors, which will be returned as well
```{r circle rand, fig.width=7, fig.height=7, fig.align="center"}
draw_color_circle(n=5,lwd=50)
```
