---
title: "Intro to my package"
output:
  rmarkdown::html_vignette:
    toc: yes
    #theme: cayman
    #toc_float: yes

vignette: >
  %\VignetteIndexEntry{Intro to my package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SHollizeckPackage)
```

# Introduction
This package contains all of the functions written in R for my PhD. These will be non thematically seperated functions. For an overview of the workflows it is probably smart to look at the markdowns generated for sample analysis.


## Colours
This section has to do with different colors functions
`make_shades()`, `plot_colours()` and `random_colours()` allows easy acces to standard requests that you have

```{r shades}
shades <- make_shades("goldenrod", 5)
```
this will generate different shades of the color "goldenrod"

which you can then visualize with
```{r plot, fig.width=7, fig.align="center"}
plot_colours(shades)
```

This function however works with any colours that you throw at it, for example 10 random colours from the function

```{r random colors, fig.width=7, fig.align="center"}
plot_colours(random_colors(10))
```

Then if you do not like the next to each other visualization, you can use `draw_color_circle()` to view how R will use them with recycling

```{r circle, fig.width=7, fig.height=7, fig.align="center"}
draw_color_circle(shades,lwd=50)
```


or directly with random colors, which will be returned as well
```{r circle rand, fig.width=7, fig.height=7, fig.align="center"}
draw_color_circle(n=5,lwd=50)
```

## Human region plotting
Sometimes it is nice to visualize, where a lesion is located in the body. In this case you can just use these functions to generate a high abstraction level plot.

### available sites
The xml provided allows the selection variety if locations which are predefined by me and common lesion sites.
```{r organs}
mappingXML <- loadXML()
sites <- getAllOrgans(mappingXML)
sites
```

### drawing
Now we can plot this human outline
```{r draw plain, fig.align="center", fig.width=7}
drawXML(mappingXML)
```

But because this is not especially entertaining, we can colour different sites

### changing the colouring
By adjusting not only the type of drawing (fill or stroke) but also the colouring we can generate an overview of leasion sites easy and efficient
```{r change style}
changePlottingStyle(mappingXML, "lung", style = "stroke", color="red")
changePlottingStyle(mappingXML, "left_lower_brain", color="orange")
```
These functions work directly on the object and just return TRUE or FALSE, if they changed something or if the change failed
Finally we have to plot the object again, like before
```{r draw colored, fig.align="center", fig.width=7}
drawXML(mappingXML)
```
